---
title: "CKD plots"
output: html_document
---

### CKD progression
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

## Import libraries
library('tidyverse')
library('kableExtra')
library('cowplot')
library('scales')

# Read in data
#setwd("C:/Users/viymah/Documents/GitHub/ckd-healthcare-use/analysis/ukka")
d = read.csv("ckd_progression_final.csv", fileEncoding="UTF-8-BOM")

# Pick out perecentages
d1 = subset(d, metric=="Percentage")

# Create stacked dataframe with 1 row per data point
d2 = rbind(
  d1 %>% mutate(count = count_2017, year = 2017),
  d1 %>% mutate(count = count_2018, year = 2018),
  d1 %>% mutate(count = count_2019, year = 2019),
  d1 %>% mutate(count = count_2020, year = 2020),
  d1 %>% mutate(count = count_2021, year = 2021),
  d1 %>% mutate(count = count_2022, year = 2022)
) %>%
  # select variables of interest
  select(start_status, end_status, count, year)

# Set factor levels for end status
d2$end_status = factor(d2$end_status, 
                       levels = c("No progression", "Dialysis", "Transplant", "Deceased"))
```

#### Plot with 'No progression' included
```{r, fig.width=9, fig.height=5}
# Generate ggplot with year as x axis and % as y axis
ggplot(d2, aes(x = year, y = count, fill = end_status)) + 
   geom_bar(stat="identity", alpha=0.9) + 
   ylab("%") + xlab("") +
   # generate facets by starting status (vertical) and ending status (horizontal)
   # switch = "y" to put the strip text on left of plot
   facet_grid(start_status ~ end_status, switch = "y" ) +
   # set colours (a good resource for finding hex codes is here: https://colorbrewer2.org)
   scale_fill_manual(values = c("#3B9AB2", "#EBCC2A","#E1AF00","#B40F20")) +
   scale_x_continuous(breaks=seq(2017, 2022, by = 1)) +
   theme_bw() + 
   theme(legend.position = "none", 
         axis.text = element_text(size=14), 
         axis.title = element_text(size=14),
         strip.background = element_blank(),
         strip.placement = "outside",
         strip.text.y.left = element_text(angle = 0),
         strip.text = element_text(size=14),
         axis.text.x = element_text(angle=45, hjust = 1)
         )
```

#### Plot with 'No progression' excluded
```{r, fig.width=8, fig.height=5}
# Generate ggplot with year as x axis and % as y axis
ggplot(subset(d2, end_status!="No progression"), aes(x = year, y = count, fill = end_status)) + 
   geom_bar(stat="identity", alpha=0.9) + 
   ylab("%") + xlab("") +
   facet_grid(start_status ~ end_status, switch="y") +
   scale_fill_manual(values = c("#EBCC2A","#E1AF00","#B40F20")) +
   scale_x_continuous(breaks=seq(2017, 2022, by = 1)) +
   theme_bw() + 
   theme(legend.position = "none", 
         axis.text = element_text(size=14), 
         axis.title = element_text(size=14),
         strip.placement = "outside",
         strip.text.y.left = element_text(angle = 0),
         strip.background = element_blank(),
         strip.text = element_text(size=14), 
         axis.text.x = element_text(angle=45, hjust = 1)
         )
```

### CKD time series
```{r}
# Read in data
d = read.csv("ckd_timeseries_final.csv")
d$Date = as.Date(d$Date, format="%d/%m/%Y")

# Create stacked dataframe with 1 row per data point
d1 = rbind(
  d %>% mutate(count = Hospital_days, outcome = "Hospital days"),
  d %>% mutate(count = ICU_days, outcome = "ICU days"),
  d %>% mutate(count = ED_days, outcome = "ED days"),
  d %>% mutate(count = OPD_appts, outcome = "OPD appts"),
  d %>% mutate(count = GP_interactions, outcome = "GP interactions")
) %>%
  # select variables of interest
  select(Date, count, outcome)
```

#### Hospital days
```{r, fig.width=5, fig.height=3}
palette = c("#3B9AB2","#EBCC2A","#E1AF00","#B40F20", "#6e016b") # a few nice colours

# function to create a plot for a selected outcome
# by wrapping the plot code in a function, you can avoid lots of copying/pasting below

single_plot = function(plot_outcome, colour_hex="#E1AF00") {
  
  d2 = subset(d1, outcome==plot_outcome)
  plot_ymin = min(d2$count, na.rm=T)*0.9
  plot_ymax = max(d2$count, na.rm=T)*1.1
  ggplot(d2, aes(x = Date, y = count)) + 
     geom_line(colour = colour_hex, size=0.8) + 
     # Label y axis by first item in outcome variable
     ylab(d2$outcome[1]) +
     # Add shaded rectangles starting 1st April for every second year (to mark cohort initiation points)
     annotate("rect", xmin = as.Date("01/04/2018", format="%d/%m/%Y"), 
              xmax = as.Date("31/03/2019", format="%d/%m/%Y"), ymin = plot_ymin, ymax = plot_ymax, alpha = .1) +
     annotate("rect", xmin = as.Date("01/04/2020", format="%d/%m/%Y"), 
              xmax = as.Date("31/03/2021", format="%d/%m/%Y"), ymin = plot_ymin, ymax = plot_ymax, alpha = .1) +
     annotate("rect", xmin = as.Date("01/04/2022", format="%d/%m/%Y"), 
              xmax = as.Date("31/03/2023", format="%d/%m/%Y"), ymin = plot_ymin, ymax = plot_ymax, alpha = .1) +
     theme_bw() + ylim(plot_ymin,plot_ymax) +
     theme(legend.position = "none", 
           axis.text = element_text(size=14), 
           axis.title = element_text(size=14)
           )
}

single_plot(plot_outcome="Hospital days", colour_hex=palette[1])
```

#### ICU days
```{r, fig.width=5, fig.height=3}
single_plot(plot_outcome="ICU days", colour_hex=palette[5])
```

#### ED days
```{r, fig.width=5, fig.height=3}
single_plot(plot_outcome="ED days", colour_hex=palette[4])
```

#### OPD appts
```{r, fig.width=5, fig.height=3}
single_plot(plot_outcome="OPD appts", colour_hex=palette[2])
```

#### GP interactions
```{r, fig.width=5, fig.height=3}
single_plot(plot_outcome="GP interactions", colour_hex=palette[3])
```

#### Combination plot
```{r, fig.width=7, fig.height=4}
d2 = d1

# Scale ICU and ED days up by 10-fold to fit on same axis
d2$count[d2$outcome=="ICU days"] = d2$count[d2$outcome=="ICU days"]*10
d2$count[d2$outcome=="ED days"] = d2$count[d2$outcome=="ED days"]*10
d2$outcome[d2$outcome=="ICU days"] = "ICU days x 10"
d2$outcome[d2$outcome=="ED days"] = "ED days x 10"

# Set plot limits
plot_ymin = min(d2$count, na.rm=T)*0.9
plot_ymax = max(d2$count, na.rm=T)*1.1

# Set factor levels for outcome
d2$outcome = factor(d2$outcome, levels = c("Hospital days", "OPD appts", "GP interactions", "ED days x 10", "ICU days x 10"))

# Generate plot
ggplot(d2, aes(x = Date, y = count, colour=outcome)) + 
     geom_line(size=0.8) + ylab("Count") +
     annotate("rect", xmin = as.Date("01/04/2018", format="%d/%m/%Y"), 
              xmax = as.Date("31/03/2019", format="%d/%m/%Y"), ymin = plot_ymin, ymax = plot_ymax, alpha = .1) +
     annotate("rect", xmin = as.Date("01/04/2020", format="%d/%m/%Y"), 
              xmax = as.Date("31/03/2021", format="%d/%m/%Y"), ymin = plot_ymin, ymax = plot_ymax, alpha = .1) +
     annotate("rect", xmin = as.Date("01/04/2022", format="%d/%m/%Y"), 
              xmax = as.Date("31/03/2023", format="%d/%m/%Y"), ymin = plot_ymin, ymax = plot_ymax, alpha = .1) +
     theme_bw() + ylim(plot_ymin,plot_ymax) + labs(colour = "Outcome") +
     scale_colour_manual(values=palette) +
     theme(legend.position = "right", 
           axis.text = element_text(size=14), 
           axis.title = element_text(size=14),
           legend.title = element_text(size=14), 
           legend.text = element_text(size=10) 
           )
```

#### Facet plot
```{r, fig.width=8, fig.height=5}
# Generate plot
ggplot(d2, aes(x = Date, y = count, colour=outcome)) + 
    facet_wrap(outcome~.) +
     geom_line(size=0.8) + ylab("Count") +
     annotate("rect", xmin = as.Date("01/04/2018", format="%d/%m/%Y"), 
              xmax = as.Date("31/03/2019", format="%d/%m/%Y"), ymin = plot_ymin, ymax = plot_ymax, alpha = .1) +
     annotate("rect", xmin = as.Date("01/04/2020", format="%d/%m/%Y"), 
              xmax = as.Date("31/03/2021", format="%d/%m/%Y"), ymin = plot_ymin, ymax = plot_ymax, alpha = .1) +
     annotate("rect", xmin = as.Date("01/04/2022", format="%d/%m/%Y"), 
              xmax = as.Date("31/03/2023", format="%d/%m/%Y"), ymin = plot_ymin, ymax = plot_ymax, alpha = .1) +
     theme_bw() + ylim(plot_ymin,plot_ymax) + labs(colour = "Outcome") +
      scale_colour_manual(values=palette) +
     theme(legend.position = "none", 
           strip.background = element_blank(),
           strip.placement = "outside",
           strip.text.y.left = element_text(angle = 0),
           strip.text = element_text(size=14),
           axis.text = element_text(size=14), 
           axis.title = element_text(size=14),
           legend.text = element_text(size=10) 
           )
```

### Dialysis/transplant populations
```{r}
# Read in data
d = read.csv("dialysis_transplant.csv", fileEncoding="UTF-8-BOM")
d$Date = as.Date(d$Date, format="%d/%m/%Y")

# Create stacked dataframe with 1 row per data point
d1 = rbind(
  d %>% mutate(count = Dialysis_OS, outcome = "Dialysis (OpenSAFELY)"),
  d %>% mutate(count = Transplant_OS, outcome = "Kidney transplants (OpenSAFLY)"),
  d %>% mutate(count = Dialysis_UKRR, outcome = "Dialysis (UK Renal Registry)"),
  d %>% mutate(count = Transplant_UKRR, outcome = "Kidney transplants (UK Renal Registry)")
) %>%
  # select variables of interest
  select(Date, count, outcome)
```

#### Prevalent kidney replacement therapy populations overlaid
```{r, fig.width=7, fig.height=4}
d2 = d1

# Set plot limits
plot_ymin = min(0)
plot_ymax = max(d2$count, na.rm=T)*1.1

# Set factor levels for outcome
d2$outcome = factor(d2$outcome, levels = c("Dialysis (OpenSAFELY)", "Kidney transplants (OpenSAFLY)", "Dialysis (UK Renal Registry)", "Kidney transplants (UK Renal Registry)"))

# Generate plot
ggplot(d2, aes(x = Date, y = count, colour=outcome)) + 
     geom_line(size=0.8) + ylab("Number of prevalent patients") + xlab("Year") +
     theme_bw() + ylim(plot_ymin,plot_ymax) + labs(colour = "Modality (data source)") +
     scale_colour_manual(values=palette) +
     theme(legend.position = "right", 
           axis.text = element_text(size=14), 
           axis.title = element_text(size=14),
           legend.title = element_text(size=14), 
           legend.text = element_text(size=10) 
           )
```
### Dialysis/transplant populations
```{r}
# Read in data
d = read.csv("access.csv", fileEncoding="UTF-8-BOM")
d$Date = as.Date(d$Date, format="%d/%m/%Y")

# Create stacked dataframe with 1 row per data point
d1 = rbind(
  d %>% mutate(count = avf, outcome = "AVF"),
  d %>% mutate(count = pd, outcome = "PD catheter")
) %>%
  # select variables of interest
  select(Date, count, outcome)
```
#### Dialysis access
```{r, fig.width=7, fig.height=4}
d2 = d1

# Set plot limits
plot_ymin = min(0)
plot_ymax = max(d2$count, na.rm=T)*1.1

# Set factor levels for outcome
d2$outcome = factor(d2$outcome, levels = c("AVF", "PD catheter"))

# Generate plot
ggplot(d2, aes(x = Date, y = count, colour=outcome)) + 
     geom_line(size=0.8) + ylab("Count") + xlab("Month") +
     theme_bw() + ylim(plot_ymin,plot_ymax) + labs(colour = "Access modality") +
     scale_colour_manual(values=palette) +
     theme(legend.position = "right", 
           axis.text = element_text(size=14), 
           axis.title = element_text(size=14),
           legend.title = element_text(size=14), 
           legend.text = element_text(size=10) 
           )
```
### CKD time series (restricted to OPD, ED & GP)
```{r}
# Read in data
d = read.csv("ckd_timeseries_ukka.csv", fileEncoding="UTF-8-BOM")
d$Date = as.Date(d$Date, format="%d/%m/%Y")

# Create stacked dataframe with 1 row per data point
d1 = rbind(
  d %>% mutate(count = ED_days, outcome = "ED days"),
  d %>% mutate(count = OPD_appts, outcome = "OPD appts"),
  d %>% mutate(count = GP_interactions, outcome = "GP interactions")
) %>%
  # select variables of interest
  select(Date, count, outcome)
```
#### Combination plot
```{r, fig.width=7, fig.height=4}
d2 = d1

# Set plot limits
plot_ymin = min(d2$count, na.rm=T)*0.9
plot_ymax = max(d2$count, na.rm=T)*1.1

# Set factor levels for outcome
d2$outcome = factor(d2$outcome, levels = c("OPD appts", "GP interactions", "ED days"))

# Generate plot
ggplot(d2, aes(x = Date, y = count, colour=outcome)) + 
     geom_line(size=0.8) + ylab("Count") +
     theme_bw() + ylim(plot_ymin,plot_ymax) + labs(colour = "Healthcare setting") +
     scale_colour_manual(values=palette) +
     theme(legend.position = "right", 
           axis.text = element_text(size=14), 
           axis.title = element_text(size=14),
           legend.title = element_text(size=14), 
           legend.text = element_text(size=10) 
           )
```
### Annual healthcare use (restricted to OPD, ED & GP)
```{r}
# Read in data
d = read.csv("annual_healthcare.csv", fileEncoding="UTF-8-BOM")
d$Date = as.Date(d$Date, format="%d/%m/%Y")

# Create stacked dataframe with 1 row per data point
d1 = rbind(
  d %>% mutate(count = ed, outcome = "ED presentations"),
  d %>% mutate(count = opd, outcome = "Outpatient appointments"),
  d %>% mutate(count = gp, outcome = "GP interactions")
) %>%
  # select variables of interest
  select(Date, count, outcome)

# Change date coding
d1$Date_factor = factor(d1$Date)
d1$Date_factor = recode_factor(d1$Date_factor, "2017-04-01" = "2016/17", "2018-04-01" = "2017/18", "2019-04-01" = "2018/19", "2020-04-01" = "2019/20", "2021-04-01" = "2020/21", "2022-04-01" = "2021/22") 

```

#### Combination bar charts
```{r, fig.width=9, fig.height=4}
d2 = d1

# Set factor levels for outcome
d2$outcome = factor(d2$outcome, levels = c("Outpatient appointments", "GP interactions", "ED presentations"))

# Generate plot
ggplot(d2, aes(x = Date_factor, y = count, fill=outcome)) + 
    facet_grid(.~outcome) + xlab("") +
     geom_bar(stat="identity") + ylab("Count") +
     theme_bw() + labs(colour = "Healthcare setting") +
     scale_fill_manual(values=palette) +
     theme(legend.position = "none", 
           strip.background = element_blank(),
           strip.placement = "outside",
           strip.text.y.left = element_text(angle = 0),
           strip.text = element_text(size=14),
           axis.text = element_text(size=14), 
           axis.text.x = element_text(size=14, angle = 45, hjust=1), 
           axis.title = element_text(size=14),
           legend.text = element_text(size=10) 
           )
```