---
title: "Relative healthcare use (Albuminuria with eGFR >60)"
output: html_document
output_dir: "C:/Users/lsh1703468/Documents/Repo/ckd-healthcare-use/results"
output_file: "relative_healthcare_use_albuminuria.html"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

## Import libraries
library('tidyverse')
library('kableExtra')
library('cowplot')
library('scales')
```

```{r}
#setwd("C:/Users/lsh1703468/Dropbox/PhD/health economics/figures")
### Annual healthcare use (restricted to OPD, ED & GP)
palette <- c("#3B9AB2", "#EBCC2A", "#E1AF00", "#B40F20", "#5DBB63", "#FF5733", "#FFC300", "#FF8C00", "#CD5C5C", "#FF1493", "#9370DB", "#6A5ACD")

# Read in data
### Suggestion 1: Read in all the data together, while defining 'group'
### group will become your vertical facet for each outcome plot
### NB some groups lack certain columns, so you may need to add blank columns filled with NAs to get this to work
d <- rbind(
  read.csv("/Users/icrueprk/Desktop/V_data/relative_healthcare_use_overall.csv", 
           sep = "\t", na.strings = "N/A") %>% mutate(group = "Overall"),
  read.csv("/Users/icrueprk/Desktop/V_data/relative_healthcare_use_ckd4.csv", 
           sep = "\t", na.strings = "N/A") %>% mutate(group = "CKD4")
)
d$Date <- as.Date(d$Date, format = "%d/%m/%Y")

# Create stacked dataframe with 1 row per data point
d1 <- rbind(
  d %>% mutate(count = ip, outcome = "Inpatient days", rate = ip, ll = ip_ll, ul = ip_ul),
  d %>% mutate(count = icu, outcome = "ICU days", rate = icu, ll = icu_ll, ul = icu_ul),
  d %>% mutate(count = ed, outcome = "ED presentations", rate = ed, ll = ed_ll, ul = ed_ul),
  d %>% mutate(count = opd, outcome = "Outpatient appointments", rate = opd, ll = opd_ll, ul = opd_ul),
  d %>% mutate(count = neph, outcome = "Nephrology appointments", rate = neph, ll = neph_ll, ul = neph_ul),
  d %>% mutate(count = gp, outcome = "GP interactions", rate = gp, ll = gp_ll, ul = gp_ul),
  d %>% mutate(count = bp, outcome = "Blood pressure measurements", rate = bp, ll = bp_ll, ul = bp_ul),
  d %>% mutate(count = uacr, outcome = "uACR measurements", rate = uacr, ll = uacr_ll, ul = uacr_ul),
  d %>% mutate(count = scr, outcome = "SCr measurements", rate = scr, ll = scr_ll, ul = scr_ul)
) %>%
  # select variables of interest
  select(Date, group, stratum, outcome, rate, ll, ul)

# Change date coding
d1$Date_factor <- factor(d1$Date)
d1$Date_factor <- recode_factor(d1$Date_factor, "2017-04-01" = "2016/17", "2018-04-01" = "2017/18", "2019-04-01" = "2018/19", "2020-04-01" = "2019/20", "2021-04-01" = "2020/21", "2022-04-01" = "2021/22") 
```

<b>[Inpatient days]{style="font-size: 20px;"}</b>

[Inpatient days (overall)]{style="font-size: 16px;"}

```{r, fig.width=8, fig.height=3, message=FALSE}
# Filter the data for "Inpatient days"
d2_ip <- d1 %>%
  filter(outcome == "Inpatient days")

d2_ip$group <- factor(d2_ip$group, levels = c("Overall", "CKD4"))
d2_ip$stratum <- factor(d2_ip$stratum, levels = c("all"))

# Generate plot
col1 = ggplot(d2_ip, aes(x = Date, y = rate)) + 
  geom_smooth(size = 0.8) + 
  facet_grid(group~.) + ### EP comment: add vertical facet 
  ylab("Inpatient days/100 patients") + 
  xlab("Year") +
  geom_smooth(aes(ymin = ll, ymax = ul), alpha = 0.2) +
  labs(colour = "Inpatient days") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  #ylim(0, 500) +
  theme(strip.background = element_blank(),
        strip.text = element_blank(), ### EP coment: add this line if you only want the facet labels on the right hand plot
        legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )
```

Inpatient days by ethnicity

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_ip <- d1 %>%
  filter(outcome == "Inpatient days")

d2_ip$group <- factor(d2_ip$group, levels = c("Overall", "CKD4"))
d2_ip$stratum <- factor(d2_ip$stratum, levels = c("White", "South Asian", "Black", "Mixed", "Other", "Unknown"))

# Generate plot
col2 = ggplot(d2_ip %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  facet_grid(group~.) + ### EP comment: add vertical facet 
  ylab(" ") + ### EP comment: y axis label removed for cols 2-5, but can be added back in
  xlab("Year") +
  labs(colour = "Inpatient days") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  #ylim(0, 500) +
  labs(color = "Ethnicity") +  # Set the legend title to "Ethnicity"
  theme(strip.background = element_blank(),
        strip.text = element_blank(), ### EP coment: add this line if you only want the facet labels on the right hand plot  
        legend.position = "bottom", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )
```

Inpatient days by IMD

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_ip <- d1 %>%
  filter(outcome == "Inpatient days")

d2_ip$group <- factor(d2_ip$group, levels = c("Overall", "CKD4"))
d2_ip$stratum <- factor(d2_ip$stratum, levels = c("1 Most deprived", "2", "3", "4", "5 Least deprived"))

# Generate plot
col3 = ggplot(d2_ip %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  facet_grid(group~.) + ### EP comment: add vertical facet 
  ylab(" ") + ### EP comment: y axis label removed for cols 2-5, but can be added back in
  xlab("Year") +
  labs(colour = "Inpatient days") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  #ylim(0, 500) +
  labs(color = "IMD") +  # Set the legend title to "Ethnicity"
  theme(strip.background = element_blank(),
        strip.text = element_blank(), ### EP coment: add this line if you only want the facet labels on the right hand plot  
        legend.position = "bottom", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

Inpatient days by region

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_ip <- d1 %>%
  filter(outcome == "Inpatient days")

d2_ip$group <- factor(d2_ip$group, levels = c("Overall", "CKD4"))
d2_ip$stratum <- factor(d2_ip$stratum, levels = c("East Midlands", "East", "London", "North East", "North West", "South East", "South West", "West Midlands", "Yorkshire and The Humber"))

# Generate plot
col4 = ggplot(d2_ip %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  facet_grid(group~.) + ### EP comment: add vertical facet 
  ylab(" ") + ### EP comment: y axis label removed for cols 2-5, but can be added back in
  xlab("Year") +
  labs(colour = "Inpatient days") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  #ylim(0, 500) +
  labs(color = "Region") +  # Set the legend title to "Ethnicity"
  theme(strip.background = element_blank(),
        strip.text = element_blank(), ### EP coment: add this line if you only want the facet labels on the right hand plot  
        legend.position = "bottom", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )
```

Inpatient days by rural/urban

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_ip <- d1 %>%
  filter(outcome == "Inpatient days")

d2_ip$group <- factor(d2_ip$group, levels = c("Overall", "CKD4"))
d2_ip$stratum <- factor(d2_ip$stratum, levels = c("Rural", "Urban"))

# Generate plot
col5 = ggplot(d2_ip %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  facet_grid(group~.) + ### EP comment: add vertical facet 
  ylab(" ") + ### EP comment: y axis label removed for cols 2-5, but can be added back in
  xlab("Year") +
  labs(colour = "Inpatient days") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  #ylim(0, 500) +
  labs(color = "Rural/urban") +  # Set the legend title to "Ethnicity"
  theme(strip.background = element_blank(),
        legend.position = "bottom", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )
```

### Full plot
```{r, fig.width=8, fig.height=3, message=FALSE}
### EP comment - adjust width and height above as needed
plot_grid(col1, col2, col3, col4, col5, 
          ncol=5, align="h", axis="tb")
```

<b>[ICU days]{style="font-size: 20px;"}</b>

[ICU days (overall)]{style="font-size: 16px;"}

```{r, fig.width=8, fig.height=3, message=FALSE}
# Filter the data for "ICU days"
d2_icu <- d1 %>%
  filter(outcome == "ICU days")

d2_icu$stratum <- factor(d2_icu$stratum, levels = c("all"))

# Generate plot
ggplot(d2_icu, aes(x = Date, y = rate)) + 
  geom_smooth(size = 0.8) + 
  ylab("ICU days/100 patients") + 
  xlab("Year") +
  geom_smooth(aes(ymin = ll, ymax = ul), alpha = 0.2) +
  labs(colour = "ICU days") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 20) +
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )
```

ICU days by ethnicity

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_icu <- d1 %>%
  filter(outcome == "ICU days")

d2_icu$stratum <- factor(d2_icu$stratum, levels = c("White", "South Asian", "Black", "Mixed", "Other", "Unknown"))

# Generate plot
ggplot(d2_icu %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("ICU days/100 patients") + 
  xlab("Year") +
  labs(colour = "ICU days") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 20) +
  labs(color = "Ethnicity") +  # Set the legend title to "Ethnicity"
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

ICU days by IMD

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_icu <- d1 %>%
  filter(outcome == "ICU days")

d2_icu$stratum <- factor(d2_icu$stratum, levels = c("1 Most deprived", "2", "3", "4", "5 Least deprived"))

# Generate plot
ggplot(d2_icu %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("ICU days/100 patients") + 
  xlab("Year") +
  labs(colour = "ICU days") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 20) +
  labs(color = "IMD") +  # Set the legend title to "Ethnicity"
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

ICU days by region

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_icu <- d1 %>%
  filter(outcome == "ICU days")

d2_icu$stratum <- factor(d2_icu$stratum, levels = c("East Midlands", "East", "London", "North East", "North West", "South East", "South West", "West Midlands", "Yorkshire and The Humber"))

# Generate plot
ggplot(d2_icu %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("ICU days/100 patients") + 
  xlab("Year") +
  labs(colour = "ICU days") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 20) +
  labs(color = "Region") +  # Set the legend title to "Ethnicity"
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

ICU days by rural/urban

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_icu <- d1 %>%
  filter(outcome == "ICU days")

d2_icu$stratum <- factor(d2_icu$stratum, levels = c("Rural", "Urban"))

# Generate plot
ggplot(d2_icu %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("ICU days/100 patients") + 
  xlab("Year") +
  labs(colour = "ICU days") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 20) +
  labs(color = "Rural/urban") + 
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

<b>[ED presentations]{style="font-size: 20px;"}</b>

[ED presentations (overall)]{style="font-size: 16px;"}

```{r, fig.width=8, fig.height=3, message=FALSE}
# Convert the "Date" column to a Date object
d1$Date <- as.Date(d1$Date, format = "%Y_%m_%d")

# Filter the data for "ED presentations" and Date not equal to the specified date
d2_ed <- d1 %>%
  filter(outcome == "ED presentations", !Date == as.Date("2017-04-01"))

d2_ed$stratum <- factor(d2_ed$stratum, levels = c("all"))

# Generate plot
ggplot(d2_ed, aes(x = Date, y = rate)) + 
  geom_smooth(size = 0.8) + 
  ylab("ED presentations/100 patients") + 
  xlab("Year") +
  geom_smooth(aes(ymin = ll, ymax = ul), alpha = 0.2) +
  labs(colour = "ED presentations") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_continuous(
    breaks = seq(as.Date("2017-04-01"), as.Date("2022-04-01"), by = "1 year"),  # Specify breaks
    labels = date_format("%Y")  # Format labels as years
  ) +
  theme_bw() + 
  ylim(0, 70) +
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )
```

ED presentations by ethnicity

```{r, fig.width=8, fig.height=3, message=FALSE}
# Convert the "Date" column to a Date object
d1$Date <- as.Date(d1$Date, format = "%Y_%m_%d")

d2_ed <- d1 %>%
  filter(outcome == "ED presentations", !Date == as.Date("2017-04-01"))

d2_ed$stratum <- factor(d2_ed$stratum, levels = c("White", "South Asian", "Black", "Mixed", "Other", "Unknown"))

# Generate plot
ggplot(d2_ed %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("ED presentations/100 patients") + 
  xlab("Year") +
  labs(colour = "ED presentations") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_continuous(
    breaks = seq(as.Date("2017-04-01"), as.Date("2022-04-01"), by = "1 year"),  # Specify breaks
    labels = date_format("%Y")  # Format labels as years
  ) +
  theme_bw() + 
  ylim(0, 70) +
  labs(color = "Ethnicity") + 
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

ED presentations by IMD

```{r, fig.width=8, fig.height=3, message=FALSE}
# Convert the "Date" column to a Date object
d1$Date <- as.Date(d1$Date, format = "%Y_%m_%d")

d2_ed <- d1 %>%
  filter(outcome == "ED presentations", !Date == as.Date("2017-04-01"))

d2_ed$stratum <- factor(d2_ed$stratum, levels = c("1 Most deprived", "2", "3", "4", "5 Least deprived"))

# Generate plot
ggplot(d2_ed %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("ED presentations/100 patients") + 
  xlab("Year") +
  labs(colour = "ED presentations") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_continuous(
    breaks = seq(as.Date("2017-04-01"), as.Date("2022-04-01"), by = "1 year"),  # Specify breaks
    labels = date_format("%Y")  # Format labels as years
  ) +
  theme_bw() + 
  ylim(0, 70) +
  labs(color = "IMD") + 
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

ED presentations by region

```{r, fig.width=8, fig.height=3, message=FALSE}
# Convert the "Date" column to a Date object
d1$Date <- as.Date(d1$Date, format = "%Y_%m_%d")

d2_ed <- d1 %>%
  filter(outcome == "ED presentations", !Date == as.Date("2017-04-01"))

d2_ed$stratum <- factor(d2_ed$stratum, levels = c("East Midlands", "East", "London", "North East", "North West", "South East", "South West", "West Midlands", "Yorkshire and The Humber"))

# Generate plot
ggplot(d2_ed %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("ED presentations/100 patients") + 
  xlab("Year") +
  labs(colour = "ED presentations") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_continuous(
    breaks = seq(as.Date("2017-04-01"), as.Date("2022-04-01"), by = "1 year"),  # Specify breaks
    labels = date_format("%Y")  # Format labels as years
  ) +
  theme_bw() + 
  ylim(0, 70) +
  labs(color = "Region") + 
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

ED presentations by rural/urban

```{r, fig.width=8, fig.height=3, message=FALSE}
# Convert the "Date" column to a Date object
d1$Date <- as.Date(d1$Date, format = "%Y_%m_%d")

d2_ed <- d1 %>%
  filter(outcome == "ED presentations", !Date == as.Date("2017-04-01"))

d2_ed$stratum <- factor(d2_ed$stratum, levels = c("Rural", "Urban"))

# Generate plot
ggplot(d2_ed %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("ED presentations/100 patients") + 
  xlab("Year") +
  labs(colour = "ED presentations") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_continuous(
    breaks = seq(as.Date("2017-04-01"), as.Date("2022-04-01"), by = "1 year"),  # Specify breaks
    labels = date_format("%Y")  # Format labels as years
  ) +
  theme_bw() + 
  ylim(0, 70) +
  labs(color = "Rural/urban") + 
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

<b>[Outpatient appointments]{style="font-size: 20px;"}</b>

[Outpatient appointments (overall)]{style="font-size: 16px;"}

```{r, fig.width=8, fig.height=3, message=FALSE}
# Convert the "Date" column to a Date object
d1$Date <- as.Date(d1$Date, format = "%Y_%m_%d")

# Filter the data for "Outpatient appointments" and Date not equal to the specified date
d2_opd <- d1 %>%
  filter(outcome == "Outpatient appointments", !Date == as.Date("2017-04-01"), !Date == as.Date("2018-04-01"))

d2_opd$stratum <- factor(d2_opd$stratum, levels = c("all"))

# Generate plot
ggplot(d2_opd, aes(x = Date, y = rate)) + 
  geom_smooth(size = 0.8) + 
  ylab("Outpatient appointments/100 patients") + 
  xlab("Year") +
  geom_smooth(aes(ymin = ll, ymax = ul), alpha = 0.2) +
  labs(colour = "Outpatient appointments") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_continuous(
    breaks = seq(as.Date("2018-04-01"), as.Date("2022-04-01"), by = "1 year"),  # Specify breaks
    labels = date_format("%Y")  # Format labels as years
  ) +
  theme_bw() + 
  ylim(0, 600) +
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )
```

Outpatient appointments by ethnicity

```{r, fig.width=8, fig.height=3, message=FALSE}
# Convert the "Date" column to a Date object
d1$Date <- as.Date(d1$Date, format = "%Y_%m_%d")

d2_opd <- d1 %>%
  filter(outcome == "Outpatient appointments", !Date == as.Date("2017-04-01"), !Date == as.Date("2018-04-01"))

d2_opd$stratum <- factor(d2_opd$stratum, levels = c("White", "South Asian", "Black", "Mixed", "Other", "Unknown"))

# Generate plot
ggplot(d2_opd %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("Outpatient appointments/100 patients") + 
  xlab("Year") +
  labs(colour = "Outpatient appointments") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_continuous(
    breaks = seq(as.Date("2017-04-01"), as.Date("2022-04-01"), by = "1 year"),  # Specify breaks
    labels = date_format("%Y")  # Format labels as years
  ) +
  theme_bw() + 
  ylim(0, 600) +
  labs(color = "Ethnicity") + 
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

Outpatient appointments by IMD

```{r, fig.width=8, fig.height=3, message=FALSE}
# Convert the "Date" column to a Date object
d1$Date <- as.Date(d1$Date, format = "%Y_%m_%d")

d2_opd <- d1 %>%
  filter(outcome == "Outpatient appointments", !Date == as.Date("2017-04-01"), !Date == as.Date("2018-04-01"))

d2_opd$stratum <- factor(d2_opd$stratum, levels = c("1 Most deprived", "2", "3", "4", "5 Least deprived"))

# Generate plot
ggplot(d2_opd %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("Outpatient appointments/100 patients") + 
  xlab("Year") +
  labs(colour = "Outpatient appointments") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_continuous(
    breaks = seq(as.Date("2017-04-01"), as.Date("2022-04-01"), by = "1 year"),  # Specify breaks
    labels = date_format("%Y")  # Format labels as years
  ) +
  theme_bw() + 
  ylim(0, 600) +
  labs(color = "IMD") + 
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

Outpatient appointments by region

```{r, fig.width=8, fig.height=3, message=FALSE}
# Convert the "Date" column to a Date object
d1$Date <- as.Date(d1$Date, format = "%Y_%m_%d")

d2_opd <- d1 %>%
  filter(outcome == "Outpatient appointments", !Date == as.Date("2017-04-01"), !Date == as.Date("2018-04-01"))

d2_opd$stratum <- factor(d2_opd$stratum, levels = c("East Midlands", "East", "London", "North East", "North West", "South East", "South West", "West Midlands", "Yorkshire and The Humber"))

# Generate plot
ggplot(d2_opd %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("Outpatient appointments/100 patients") + 
  xlab("Year") +
  labs(colour = "Outpatient appointments") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_continuous(
    breaks = seq(as.Date("2017-04-01"), as.Date("2022-04-01"), by = "1 year"),  # Specify breaks
    labels = date_format("%Y")  # Format labels as years
  ) +
  theme_bw() + 
  ylim(0, 600) +
  labs(color = "Region") + 
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

Outpatient appointments by rural/urban

```{r, fig.width=8, fig.height=3, message=FALSE}
# Convert the "Date" column to a Date object
d1$Date <- as.Date(d1$Date, format = "%Y_%m_%d")

d2_opd <- d1 %>%
  filter(outcome == "Outpatient appointments", !Date == as.Date("2017-04-01"), !Date == as.Date("2018-04-01"))

d2_opd$stratum <- factor(d2_opd$stratum, levels = c("Rural", "Urban"))

# Generate plot
ggplot(d2_opd %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("Outpatient appointments/100 patients") + 
  xlab("Year") +
  labs(colour = "Outpatient appointments") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_continuous(
    breaks = seq(as.Date("2017-04-01"), as.Date("2022-04-01"), by = "1 year"),  # Specify breaks
    labels = date_format("%Y")  # Format labels as years
  ) +
  theme_bw() + 
  ylim(0, 600) +
  labs(color = "Rural/urban") + 
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

<b>[Nephrology appointments]{style="font-size: 20px;"}</b>

[Nephrology appointments (overall)]{style="font-size: 16px;"}

```{r, fig.width=8, fig.height=3, message=FALSE}
# Convert the "Date" column to a Date object
d1$Date <- as.Date(d1$Date, format = "%Y_%m_%d")

# Filter the data for "Nephrology appointments" and Date not equal to the specified date
d2_neph <- d1 %>%
  filter(outcome == "Nephrology appointments", !Date == as.Date("2017-04-01"), !Date == as.Date("2018-04-01"))

d2_neph$stratum <- factor(d2_neph$stratum, levels = c("all"))

# Generate plot
ggplot(d2_neph, aes(x = Date, y = rate)) + 
  geom_smooth(size = 0.8) + 
  ylab("Nephrology appointments/100 patients") + 
  xlab("Year") +
  geom_smooth(aes(ymin = ll, ymax = ul), alpha = 0.2) +
  labs(colour = "Nephrology appointments") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_continuous(
    breaks = seq(as.Date("2018-04-01"), as.Date("2022-04-01"), by = "1 year"),  # Specify breaks
    labels = date_format("%Y")  # Format labels as years
  ) +
  theme_bw() + 
  ylim(0, 25) +
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )
```

Nephrology appointments by ethnicity

```{r, fig.width=8, fig.height=3, message=FALSE}
# Convert the "Date" column to a Date object
d1$Date <- as.Date(d1$Date, format = "%Y_%m_%d")

d2_neph <- d1 %>%
  filter(outcome == "Nephrology appointments", !Date == as.Date("2017-04-01"), !Date == as.Date("2018-04-01"))

d2_neph$stratum <- factor(d2_neph$stratum, levels = c("White", "South Asian", "Black", "Mixed", "Other", "Unknown"))

# Generate plot
ggplot(d2_neph %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("Nephrology appointments/100 patients") + 
  xlab("Year") +
  labs(colour = "Nephrology appointments") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_continuous(
    breaks = seq(as.Date("2017-04-01"), as.Date("2022-04-01"), by = "1 year"),  # Specify breaks
    labels = date_format("%Y")  # Format labels as years
  ) +
  theme_bw() + 
  ylim(0, 25) +
  labs(color = "Ethnicity") + 
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

Nephrology appointments by IMD

```{r, fig.width=8, fig.height=3, message=FALSE}
# Convert the "Date" column to a Date object
d1$Date <- as.Date(d1$Date, format = "%Y_%m_%d")

d2_neph <- d1 %>%
  filter(outcome == "Nephrology appointments", !Date == as.Date("2017-04-01"), !Date == as.Date("2018-04-01"))

d2_neph$stratum <- factor(d2_neph$stratum, levels = c("1 Most deprived", "2", "3", "4", "5 Least deprived"))

# Generate plot
ggplot(d2_neph %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("Nephrology appointments/100 patients") + 
  xlab("Year") +
  labs(colour = "Nephrology appointments") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_continuous(
    breaks = seq(as.Date("2017-04-01"), as.Date("2022-04-01"), by = "1 year"),  # Specify breaks
    labels = date_format("%Y")  # Format labels as years
  ) +
  theme_bw() + 
  ylim(0, 25) +
  labs(color = "IMD") + 
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

Nephrology appointments by region

```{r, fig.width=8, fig.height=3, message=FALSE}
# Convert the "Date" column to a Date object
d1$Date <- as.Date(d1$Date, format = "%Y_%m_%d")

d2_neph <- d1 %>%
  filter(outcome == "Nephrology appointments", !Date == as.Date("2017-04-01"), !Date == as.Date("2018-04-01"))

d2_neph$stratum <- factor(d2_neph$stratum, levels = c("East Midlands", "East", "London", "North East", "North West", "South East", "South West", "West Midlands", "Yorkshire and The Humber"))

# Generate plot
ggplot(d2_neph %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("Nephrology appointments/100 patients") + 
  xlab("Year") +
  labs(colour = "Nephrology appointments") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_continuous(
    breaks = seq(as.Date("2017-04-01"), as.Date("2022-04-01"), by = "1 year"),  # Specify breaks
    labels = date_format("%Y")  # Format labels as years
  ) +
  theme_bw() + 
  ylim(0, 25) +
  labs(color = "Region") + 
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

Nephrology appointments by rural/urban

```{r, fig.width=8, fig.height=3, message=FALSE}
# Convert the "Date" column to a Date object
d1$Date <- as.Date(d1$Date, format = "%Y_%m_%d")

d2_neph <- d1 %>%
  filter(outcome == "Nephrology appointments", !Date == as.Date("2017-04-01"), !Date == as.Date("2018-04-01"))

d2_neph$stratum <- factor(d2_neph$stratum, levels = c("Rural", "Urban"))

# Generate plot
ggplot(d2_neph %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("Nephrology appointments/100 patients") + 
  xlab("Year") +
  labs(colour = "Nephrology appointments") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_continuous(
    breaks = seq(as.Date("2017-04-01"), as.Date("2022-04-01"), by = "1 year"),  # Specify breaks
    labels = date_format("%Y")  # Format labels as years
  ) +
  theme_bw() + 
  ylim(0, 25) +
  labs(color = "Rural/urban") + 
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

<b>[GP interactions]{style="font-size: 20px;"}</b>

[GP interactions (overall)]{style="font-size: 16px;"}

```{r, fig.width=8, fig.height=3, message=FALSE}
# Filter the data for "GP interactions"
d2_gp <- d1 %>%
  filter(outcome == "GP interactions")

d2_gp$stratum <- factor(d2_gp$stratum, levels = c("all"))

# Generate plot
ggplot(d2_gp, aes(x = Date, y = rate)) + 
  geom_smooth(size = 0.8) + 
  ylab("GP interactions/100 patients") + 
  xlab("Year") +
  geom_smooth(aes(ymin = ll, ymax = ul), alpha = 0.2) +
  labs(colour = "GP interactions") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 1600) +
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )
```

GP interactions by ethnicity

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_gp <- d1 %>%
  filter(outcome == "GP interactions")

d2_gp$stratum <- factor(d2_gp$stratum, levels = c("White", "South Asian", "Black", "Mixed", "Other", "Unknown"))

# Generate plot
ggplot(d2_gp %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("GP interactions/100 patients") + 
  xlab("Year") +
  labs(colour = "GP interactions") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 1600) +
  labs(color = "Ethnicity") +  # Set the legend title to "Ethnicity"
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

GP interactions by IMD

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_gp <- d1 %>%
  filter(outcome == "GP interactions")

d2_gp$stratum <- factor(d2_gp$stratum, levels = c("1 Most deprived", "2", "3", "4", "5 Least deprived"))

# Generate plot
ggplot(d2_gp %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("GP interactions/100 patients") + 
  xlab("Year") +
  labs(colour = "GP interactions") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 1600) +
  labs(color = "IMD") +  # Set the legend title to "Ethnicity"
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

GP interactions by region

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_gp <- d1 %>%
  filter(outcome == "GP interactions")

d2_gp$stratum <- factor(d2_gp$stratum, levels = c("East Midlands", "East", "London", "North East", "North West", "South East", "South West", "West Midlands", "Yorkshire and The Humber"))

# Generate plot
ggplot(d2_gp %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("GP interactions/100 patients") + 
  xlab("Year") +
  labs(colour = "GP interactions") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 1600) +
  labs(color = "Region") +  # Set the legend title to "Ethnicity"
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

GP interactions by rural/urban

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_gp <- d1 %>%
  filter(outcome == "GP interactions")

d2_gp$stratum <- factor(d2_gp$stratum, levels = c("Rural", "Urban"))

# Generate plot
ggplot(d2_gp %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("GP interactions/100 patients") + 
  xlab("Year") +
  labs(colour = "GP interactions") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 1600) +
  labs(color = "Rural/urban") + 
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

<b>[Blood pressure measurements]{style="font-size: 20px;"}</b>

[Blood pressure measurements (overall)]{style="font-size: 16px;"}

```{r, fig.width=8, fig.height=3, message=FALSE}
# Filter the data for "Blood pressure measurements"
d2_bp <- d1 %>%
  filter(outcome == "Blood pressure measurements")

d2_bp$stratum <- factor(d2_bp$stratum, levels = c("all"))

# Generate plot
ggplot(d2_bp, aes(x = Date, y = rate)) + 
  geom_smooth(size = 0.8) + 
  ylab("Blood pressure measurements/100 patients") + 
  xlab("Year") +
  geom_smooth(aes(ymin = ll, ymax = ul), alpha = 0.2) +
  labs(colour = "Blood pressure measurements") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 100) +
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )
```

Blood pressure measurements by ethnicity

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_bp <- d1 %>%
  filter(outcome == "Blood pressure measurements")

d2_bp$stratum <- factor(d2_bp$stratum, levels = c("White", "South Asian", "Black", "Mixed", "Other", "Unknown"))

# Generate plot
ggplot(d2_bp %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("Blood pressure measurements/100 patients") + 
  xlab("Year") +
  labs(colour = "Blood pressure measurements") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 100) +
  labs(color = "Ethnicity") +  # Set the legend title to "Ethnicity"
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

Blood pressure measurements by IMD

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_bp <- d1 %>%
  filter(outcome == "Blood pressure measurements")

d2_bp$stratum <- factor(d2_bp$stratum, levels = c("1 Most deprived", "2", "3", "4", "5 Least deprived"))

# Generate plot
ggplot(d2_bp %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("Blood pressure measurements/100 patients") + 
  xlab("Year") +
  labs(colour = "Blood pressure measurements") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 100) +
  labs(color = "IMD") +  # Set the legend title to "Ethnicity"
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

Blood pressure measurements by region

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_bp <- d1 %>%
  filter(outcome == "Blood pressure measurements")

d2_bp$stratum <- factor(d2_bp$stratum, levels = c("East Midlands", "East", "London", "North East", "North West", "South East", "South West", "West Midlands", "Yorkshire and The Humber"))

# Generate plot
ggplot(d2_bp %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("Blood pressure measurements/100 patients") + 
  xlab("Year") +
  labs(colour = "Blood pressure measurements") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 100) +
  labs(color = "Region") +  # Set the legend title to "Ethnicity"
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

Blood pressure measurements by rural/urban

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_bp <- d1 %>%
  filter(outcome == "Blood pressure measurements")

d2_bp$stratum <- factor(d2_bp$stratum, levels = c("Rural", "Urban"))

# Generate plot
ggplot(d2_bp %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("Blood pressure measurements/100 patients") + 
  xlab("Year") +
  labs(colour = "Blood pressure measurements") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 100) +
  labs(color = "Rural/urban") + 
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

<b>[uACR measurements]{style="font-size: 20px;"}</b>

[uACR measurements (overall)]{style="font-size: 16px;"}

```{r, fig.width=8, fig.height=3, message=FALSE}
# Filter the data for "uACR measurements"
d2_uacr <- d1 %>%
  filter(outcome == "uACR measurements")

d2_uacr$stratum <- factor(d2_uacr$stratum, levels = c("all"))

# Generate plot
ggplot(d2_uacr, aes(x = Date, y = rate)) + 
  geom_smooth(size = 0.8) + 
  ylab("uACR measurements/100 patients") + 
  xlab("Year") +
  geom_smooth(aes(ymin = ll, ymax = ul), alpha = 0.2) +
  labs(colour = "uACR measurements") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 60) +
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )
```

uACR measurements by ethnicity

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_uacr <- d1 %>%
  filter(outcome == "uACR measurements")

d2_uacr$stratum <- factor(d2_uacr$stratum, levels = c("White", "South Asian", "Black", "Mixed", "Other", "Unknown"))

# Generate plot
ggplot(d2_uacr %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("uACR measurements/100 patients") + 
  xlab("Year") +
  labs(colour = "uACR measurements") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 60) +
  labs(color = "Ethnicity") +  # Set the legend title to "Ethnicity"
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

uACR measurements by IMD

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_uacr <- d1 %>%
  filter(outcome == "uACR measurements")

d2_uacr$stratum <- factor(d2_uacr$stratum, levels = c("1 Most deprived", "2", "3", "4", "5 Least deprived"))

# Generate plot
ggplot(d2_uacr %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("uACR measurements/100 patients") + 
  xlab("Year") +
  labs(colour = "uACR measurements") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 60) +
  labs(color = "IMD") +  # Set the legend title to "Ethnicity"
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

uACR measurements by region

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_uacr <- d1 %>%
  filter(outcome == "uACR measurements")

d2_uacr$stratum <- factor(d2_uacr$stratum, levels = c("East Midlands", "East", "London", "North East", "North West", "South East", "South West", "West Midlands", "Yorkshire and The Humber"))

# Generate plot
ggplot(d2_uacr %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("uACR measurements/100 patients") + 
  xlab("Year") +
  labs(colour = "uACR measurements") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 60) +
  labs(color = "Region") +  # Set the legend title to "Ethnicity"
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

uACR measurements by rural/urban

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_uacr <- d1 %>%
  filter(outcome == "uACR measurements")

d2_uacr$stratum <- factor(d2_uacr$stratum, levels = c("Rural", "Urban"))

# Generate plot
ggplot(d2_uacr %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("uACR measurements/100 patients") + 
  xlab("Year") +
  labs(colour = "uACR measurements") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 60) +
  labs(color = "Rural/urban") + 
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

<b>[SCr measurements]{style="font-size: 20px;"}</b>

[SCr measurements (overall)]{style="font-size: 16px;"}

```{r, fig.width=8, fig.height=3, message=FALSE}
# Filter the data for "SCr measurements"
d2_scr <- d1 %>%
  filter(outcome == "SCr measurements")

d2_scr$stratum <- factor(d2_scr$stratum, levels = c("all"))

# Generate plot
ggplot(d2_scr, aes(x = Date, y = rate)) + 
  geom_smooth(size = 0.8) + 
  ylab("SCr measurements/100 patients") + 
  xlab("Year") +
  geom_smooth(aes(ymin = ll, ymax = ul), alpha = 0.2) +
  labs(colour = "SCr measurements") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 100) +
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = 0),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )
```

SCr measurements by ethnicity

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_scr <- d1 %>%
  filter(outcome == "SCr measurements")

d2_scr$stratum <- factor(d2_scr$stratum, levels = c("White", "South Asian", "Black", "Mixed", "Other", "Unknown"))

# Generate plot
ggplot(d2_scr %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("SCr measurements/100 patients") + 
  xlab("Year") +
  labs(colour = "SCr measurements") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 100) +
  labs(color = "Ethnicity") +  # Set the legend title to "Ethnicity"
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

SCr measurements by IMD

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_scr <- d1 %>%
  filter(outcome == "SCr measurements")

d2_scr$stratum <- factor(d2_scr$stratum, levels = c("1 Most deprived", "2", "3", "4", "5 Least deprived"))

# Generate plot
ggplot(d2_scr %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("SCr measurements/100 patients") + 
  xlab("Year") +
  labs(colour = "SCr measurements") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 100) +
  labs(color = "IMD") +  # Set the legend title to "Ethnicity"
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

SCr measurements by region

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_scr <- d1 %>%
  filter(outcome == "SCr measurements")

d2_scr$stratum <- factor(d2_scr$stratum, levels = c("East Midlands", "East", "London", "North East", "North West", "South East", "South West", "West Midlands", "Yorkshire and The Humber"))

# Generate plot
ggplot(d2_scr %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("SCr measurements/100 patients") + 
  xlab("Year") +
  labs(colour = "SCr measurements") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 100) +
  labs(color = "Region") +  # Set the legend title to "Ethnicity"
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```

SCr measurements by rural/urban

```{r, fig.width=8, fig.height=3, message=FALSE}
d2_scr <- d1 %>%
  filter(outcome == "SCr measurements")

d2_scr$stratum <- factor(d2_scr$stratum, levels = c("Rural", "Urban"))

# Generate plot
ggplot(d2_scr %>% filter(!is.na(stratum)), aes(x = Date, y = rate, group = stratum, color = stratum)) + 
  geom_line(size = 0.8) + 
  ylab("SCr measurements/100 patients") + 
  xlab("Year") +
  labs(colour = "SCr measurements") +
  scale_colour_manual(values = palette) +
  scale_fill_manual(values = palette, guide = FALSE) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Specify date breaks and format
  theme_bw() + 
  ylim(0, 100) +
  labs(color = "Rural/urban") + 
  theme(legend.position = "right", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10),
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10),
        axis.text.x = element_text(size = 10, hjust = -0.5),  # Center x-axis labels
        axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

```
